Vragenlijst thesis evaluatie

### 2015-08-09 doc/template/chap-5.tex
Matthias opmerkingen

This chapter provides the reader with an introduction to the general context of the work presented in this paper.  Section 2.1 introduces the reader into the basic concepts of cyber security and the kind of cyber security threats that are in scope for this work. Section 2.2 then introduces the reader into the main principles of game theory. Subsequently, section 2.3 introduces the reader to the FlipIt game: the game that will be used to model cyber security attacks of a periodic nature, including a delay.  Finally, section 2.4 gives an overview of the related work, and how the research presented in this paper compares to existing results.

\section{What is security?}

@@

Information security is the generic term for data protection stored on a computer controlled device such as computers and smartphones, as well as public and private computer networks, including the entire Internet. 
Security is a general term that encompasses several dimensions. More specifically, information security has three fundamental key objectives:

@@

 %The purpose of security is to give certainty that data will not be removed without authorization (Confidentiality) that the data is always accessible (Availability), and that data can not be read or altered by someone who does not have the authorization (Integrity). 
 ~~\\
 These key attributes are also known as the CIA triad. They are the fundamental security objectives for securing data, information and computing services. \\
 \\
Information security can be divided into two main sub categories. One of them is cyber security, also known as computer security. This is the process of applying security tools to ensure confidentiality, integrity, and availability of data. It is an attempt to protect websites, servers, data, applications, operating systems and all assets that need protection in a computer system.  Some of these tools may include detection, identification or removal tools. A detection tool will determine if an infection has taken place and will trace the threat. An identification tool will try to identify the threat to be able to know how to remove it. A removal tool will remove the threat from the system (once it has been identified) so that it cannot spread any further. \\
The other category is network or internet security. This sub category of information security protects data during transmission. While cyber security and network security address different aspects, they partially overlap as well. For example, a virus can be physically dropped on a computer network using a USB stick, but it can also arrive over the internet. Either way internal computer security measurements have to be taken to recover from the virus. In this paper we focus on scenarios where a network has to be defended against attacks to ensure confidentiality, integrity and availability of data. The work presented in this paper therefore belongs to the domain of cyber security.

@@

In order to keep a system secure and to be able to apply security tools, it is important to mitigate the possible threats. The possible threats can take many forms, the most common being: spam, malware, spoofing, phishing and  DDoS attacks.  In the context of cyber security, the terms `threat'  and `attack' are often used interchangeably, referring to more or less the same thing. The meaning of these two terms, however, differ slightly from one another. The former refers to anything that can breach security and cause possible harm. It is a possible danger that can exploit a vulnerability. The latter is an assault on computer security that originates from a threat. It is an intelligent act that deliberately tries to breach security through vulnerabilities.  \\

@@

\begin{description}
\item \textit{Virus}: This is a malicious piece of code that replicates itself and tries to spread in order  to infect other systems or files. A typical virus will attach itself to a program, or an executable content on a computer. The \textit{I love you} virus is an example of a virus where the virus attached itself as an executable to a mail. It propagated by using the mailing systems. When a victim opened an email with the \textit{I love you} virus in the annex, the virus spread itself by sending a mail to everyone in the victim's contact list.

@@

\end{description}
~~\\
As proposed by Kasperksy \cite{APTKaspersky} ,threats caused by the malware described above can be divided into three main categories: known threats (70\%), unknown threats (29\%) and advanced threats (1\%).

@@

@@

An Advanced Persistent Threat (referred to for the remainder of this work as APT) is a persistent targeted attack that tries to penetrate a network to cause harm while staying unseen for a long period of time. The motive of an APT is mostly cyber espionage, stealing sensitive data, sabotage or other kinds of ideological attacks. APT's are `advanced' because these attacks are well funded and because the attacker (usually) needs a great amount of expertise to successfully penetrate a network. Not all APT's are technically advanced though. The attacker can also try to exploit known vulnerabilities, in the hope that his target has not yet secured itself against them. \\
`Persistent' refers to the fact that the attacker isn't trying to gain immediate results, and the attacker won't stop trying after one failed attempt. The attack can be spread over several years, taking multiple steps.  \\
An APT can be a mix of different types of malware and may use various propagation methods. \\
% like the way a virus, worm or trojan horse propagates. \\
%
%Some examples of the biggest most rare APTs are listed to get an understanding of what APTs are capable of and how long they can stay unseen. [\todo{site kaspersky apt}] 
%
%\subsubsection{Equation}
%Equation is a complex cyberattack platform where the first known sample is from 2002, but it was only discovered 12 years later in 2014. This APT propagates through usb drives, cd or physical media. It will search for exploits and will self-replicate itself to spread the infection. The purpose of this virus is to steal data and cyberespionage. 
%
%\subsubsection{Regin}
%
%\subsubsection{Flame}
%Way of propagation through USB drives, LAN spreading. purpose cyber espionage.
%
%\subsubsection{Black energy}
% purpose cyber espionage and DDoS, data wiping. prop usb lan

According to a security survey of Kaspersky \cite{SurveyKaspersky}  the damage of one successful targeted attack against a large company can exceed 2.5 million dollars. As such, companies need a defence mechanism to defend themselves against APT's. As previously stated, simple detection and identification tools are insufficient to protect oneself against APT's, and a removal tool will only work if the threat has been identified. To mitigate these kind of attacks another security countermeasure is needed. \\
%This is where the researchers of RSA come into the picture. \todo{deze paper gaat zien of de game theoretische model kan leiden tot resultaten die kunnen helpen in het verdedigen tegen APTs}
This paper proposes an appropriate game-theoretical modelling of defending a network against APT's and will analyse it in order to draw the necessary strategic conclusions to mitigate these kind of attacks.

\section{A Brief Introduction in Game Theory}
\label{Cha1:briefintro}
Game theory is a mathematical study to analyse interactions between independent and self-interested agents. To get an understanding of the most important concepts of game theory, a short introduction based on the work of 
\cite{leyton2008essentials} and \cite{Coursera} is given in this section. For a more detailed and complete introduction to game theory, the reader is referred to 
\cite{leyton2008essentials}.  \\
%In section \ref{cha1:FlipItGame} an overview of the FlipIt game is given with the definitions and concepts that will be used throughout the paper. 
%The last section \ref{ch1:extendedWork} will cover the extensions and additions already made on FlipIt. \\
%------------------------------------------------%
%            Intro Game Theory 					 %
%------------------------------------------------%
Game theory is a mathematical way of modelling the interactions between two or more agents where the outcomes depend on what each agent does and how these interactions should be structured to lead to good outcomes. Game theory therefore has important applications in many areas such as economics, politics, biology, computer science, philosophy and a variety of other disciplines. It gained recognition during the Second World War, when Oskar Morgenstern and John von Neumann both published a book on game theory, titled "Theory of Games and Economic Behavior" in 1944 \cite{von1944theory}. This book addressed the mathematical analysis of a series of thinking games. A distinction was made between games in which the strategies and the utility factor of the opponent have no effect on finding the best strategies (e.g. chess) and games wherein this factor does have an influence (e.g. poker). John Nash also played a major role in the history of game theory. He was one of the mathematicians who has formalized game theory. The Nash equilibrium, a common solution concept of a non-cooperative game, was named after him.
~~\\
%Every agent has different levels of happiness for the different outcomes.
%self interested meaning

One of the underlying assumptions game theory is that the players of the game are independent and self-interested. This does not necessarily mean that they want to harm other agents or that they only care about themselves. 
%utility function meaning 
Instead it means that each agent has preferences about which states of the world he likes. These preferences are mapped to natural numbers and are called the utility functions. The numbers are interpreted as a mathematical measure that tells how much an agent likes or dislikes the states of the world. \\
%Cooperative and non cooperative games
In a decision game-theoretic approach an agent will try to act in such a way as to maximise his expected or average utility function. It becomes more complicated when two or more agents want to maximise their utility and when actions of an agent can affect other agents' utilities. In this kind of game, the basic modelling unit is the group of agents. It is referred to as \textit{non-cooperative game theory}. In the individualistic approach the basic modelling is only one agent. This type of game is referred to as \textit{cooperative game theory}.

@@

%John Nash speelde ook een grote rol in de geschiedenis van de speltheorie. Hij is een van de wiskundigen geweest die speltheorie geformaliseerd heeft. Het Nash evenwicht werd naar hem vernoemd. Een Nash evenwicht wordt gezien als een evenwicht tussen beide spelers zodat ze allebei de beste tactiek kiezen en niet meer veranderen als de andere van tactiek veranderen. John Nash breide de theorie over het Nash evenwicht in een paper nog uit met gemengde strategieën. In 1994 kreeg John Nash samen met twee andere wiskundigen gespecialiseerd op het vlak van speltheorie de Nobelprijs voor de economie op basis van hun prestaties in de niet-coöperatieve speltheorie. . Over John Nash is een prachtige film 
\subsubsection{Best response and Nash Equilibrium}
One of the solution concepts in Game Theory for non-cooperative games that will be used in this paper is a Nash Equilibrium. A Nash Equilibrium is a subset of outcomes that can be interesting to analyse a game. To define this concept we first introduce the concept of best response. The best response for a player is the action of a player that maximizes it's pay-off for any given action of the other player. We define $Opt_{i}$ as the best response function for player \textit{i}. The best response for player \textit{1} is: $a_{1} = Opt_{1}(a_{2})$, given that $a_{2}$ is an action of player 2. For a Nash Equilibrium each player has a list of actions and each player's action maximizes his or her pay-off given the actions of the other players. Nobody has the incentive to change his or her action if an equilibrium profile is played. We have a Nash Equilibrium for the pair $(a_{1}^{*},a_{2}^{*})$ when $a_{1}^{*} = Opt_{1}(a_{2}^{*})$ and $a_{2}^{*} = Opt_{2}(a_{1}^{*})$.\\

An example to explain a Nash equilibrium of a two-player game is the prison dilemma. In this game there are two players who are both rational and both of them have committed a crime. `Rational' means that they want the best for themselves and it is not their purpose to do harm to others. Both are locked in a separate room and they cannot tell in advance to each other what they are going to say. Each of them can betray the other or they can support each other and remain silent. If a player confesses, he will either be imprisoned for 3 years or go free, depending on what the other does. If the player is silent, he will either be imprisoned for 5 years or one year, depending on what the other does.  \\ \todo{nakijken met praten, bekennen of andere veraden?}

@@

If there is no feedback for either player, he will play in the same manner against every opponent. The strategy is then called \textit{non-adaptive} because the playing strategy is not dependent on the opponents movements. An interesting subclass of the non-adaptive strategies is the one where the time intervals between two consecutive moves are generated by a renewal process \todo{renewal beter uitleggen}. An example of such renewal strategy is the periodic strategy where the time between two consecutive moves of the players are a fixed interval. An exponential strategy is a renewal strategy in which the interval between two consecutive moves is exponentially distributed. \\

@@

\subsubsection{Results of the FlipIt game}
The study of the different strategies by means of FlipIt framework allows to derive a number of interesting results \cite{FlipIt}:  
\begin{itemize}
\item periodic strategy strongly dominates the other renewal strategies if the opponent has a periodic or non-arithmetic renewal strategy. This means that it is always advantageous for the opponent to play periodically against a player with a non-adaptive strategy;
\item periodic games are disadvantageous against players following a Last Move adaptive strategy;
\item if a defender facing an LM attacker and with a cost much lower than the attacker, he can play with a periodic rate that is fast enough he'll force the attacker to drop out;
\item a defender facing an LM attacker has to play with a randomized strategy e.g. exponential strategy;
\item any amount of feedback about the opponent received during the game, benefits to a player.
\end{itemize}

>>>>

This chapter provides the reader with an introduction to the general context of the work presented in this paper.  Section 2.1 introduces the reader into the basic concepts of cyber security and the kind of cyber security threats that are in scope of this work. Section 2.2 then introduces the reader into the main principles of game theory. Subsequently, section 2.3 introduces the reader to the FlipIt game: this game will be used to model cyber security attacks of a periodic nature, including a delay.  Finally, section 2.4 gives an overview of the related work, and how the research presented in this paper compares to existing results.
%- Remark: to the reader weg
\section{What is security?}

@@

Information security is the generic term for protection of data stored on a computer controlled device such as computers and smartphones, as well as public and private computer networks, including the entire Internet. 
Security is a general term that encompasses several dimensions. More specifically, information security has three fundamental key objectives:

@@

 %The purpose of security is to give certainty that data will not be removed without authorization (Confidentiality) that the data is always accessible (Availability), and that data can not be read or altered by someone who does not have the authorization (Integrity). 
 ~~\\
 These key attributes are also known as the CIA triad. They are the fundamental security objectives for securing data, information and computing services. \\
 \\
Information security can be divided into two main subcategory. One of them is cyber security, also known as computer security. This is the process of applying security tools to ensure confidentiality, integrity, and availability of data. It is an attempt to protect websites, servers, data, applications, operating systems and all assets that need protection in a computer system.  Some of these tools may include detection, identification or removal tools. A detection tool will determine if an infection has taken place and will trace the threat. An identification tool will try to identify the threat to be able to know how to remove it. A removal tool will remove the threat from the system (once it has been identified) so that it cannot spread any further. \\
The other category is network or internet security. This sub category of information security protects data during transmission. While cyber security and network security address different aspects, they partially overlap as well. For example, a virus can be physically dropped on a computer network using a USB stick, but it can also arrive over the internet. Either way internal computer security measurements have to be taken to recover from the virus. In this paper we focus on scenarios where a network has to be defended against attacks to ensure confidentiality, integrity and availability of data. The work presented in this paper therefore belongs to the domain of cyber security.

@@

%In order to keep a system secure and to be able to apply security tools, it is important to mitigate the possible threats. -Remark-Zegt te weinig volgens Matthias 
The possible threats can take many forms, the most common being: spam, malware, spoofing, phishing and  DDoS attacks.  In the context of cyber security, the terms `threat'  and `attack' are often used interchangeably, referring to more or less the same thing. The meaning of these two terms, however, differ slightly from one another. The former refers to anything that can breach security and cause possible harm. It is a possible danger that can exploit a vulnerability. The latter is an assault on computer security that originates from a threat. It is an intelligent act that deliberately tries to breach security through vulnerabilities.  \\

@@

\begin{description}
\item \textit{Virus}: This is a malicious piece of code that replicates itself and tries to spread in order  to infect other systems or files. A typical virus will attach itself to a program, or executable content on a computer. The \textit{I love you} virus is an example of a virus where the virus attached itself as an executable to a mail. It propagated by using the mailing systems. When a victim opened an email with the \textit{I love you} virus in the annex, the virus spread itself by sending a mail to everyone in the victim's contact list.

@@

\end{description}
~~\\
As proposed by Kasperksy \cite{APTKaspersky}, threats caused by the malware described above can be divided into three main categories: known threats (70\%), unknown threats (29\%) and advanced threats (1\%).

@@

%-Remark- APTs en niet APT's

@@

An Advanced Persistent Threat (referred to for the remainder of this work as APT) is a persistent targeted attack that tries to penetrate a network to cause harm while staying unseen for a long period of time. The motive of an APT is mostly cyber espionage, stealing sensitive data, sabotage or other kinds of ideological attacks. APTs are `advanced' because these attacks are well funded and because the attacker (usually) needs a great amount of expertise to successfully penetrate a network. Not all APTs are technically advanced though. The attacker can also try to exploit known vulnerabilities, in the hope that his target has not yet secured itself against them. \\
`Persistent' refers to the fact that the attacker isn't trying to gain immediate results, and the attacker won't stop trying after one failed attempt. The attack can be spread over several years, taking multiple steps.  \\
An APT can be a mix of different types of malware and may use various propagation methods. \\
% like the way a virus, worm or trojan horse propagates. \\
%
%Some examples of the biggest most rare APTs are listed to get an understanding of what APTs are capable of and how long they can stay unseen. [\todo{site kaspersky apt}] 
%
%\subsubsection{Equation}
%Equation is a complex cyberattack platform where the first known sample is from 2002, but it was only discovered 12 years later in 2014. This APT propagates through usb drives, cd or physical media. It will search for exploits and will self-replicate itself to spread the infection. The purpose of this virus is to steal data and cyberespionage. 
%
%\subsubsection{Regin}
%
%\subsubsection{Flame}
%Way of propagation through USB drives, LAN spreading. purpose cyber espionage.
%
%\subsubsection{Black energy}
% purpose cyber espionage and DDoS, data wiping. prop usb lan

According to a security survey of Kaspersky \cite{SurveyKaspersky}  the damage of one successful targeted attack against a large company can exceed 2.5 million dollars. As such, companies need a defence mechanism to defend themselves against APTs. As previously stated, simple detection and identification tools are insufficient to protect oneself against APTs, and a removal tool will only work if the threat has been identified. To mitigate these kind of attacks another security countermeasure is needed. \\
%This is where the researchers of RSA come into the picture. \todo{deze paper gaat zien of de game theoretische model kan leiden tot resultaten die kunnen helpen in het verdedigen tegen APTs}
This paper proposes an appropriate game-theoretical modelling of defending a network against APTs and will analyse it in order to draw the necessary strategic conclusions to mitigate these kind of attacks.

\section{A Brief Introduction in Game Theory}
\label{Cha1:briefintro}
%-Remar- based on the work of - Matthias zegt namen erbij zetten
Game theory is a mathematical study to analyse interactions between independent and self-interested agents. To get an understanding of the most important concepts of game theory, a short introduction based on the work of 
\cite{leyton2008essentials} and \cite{Coursera} is given in this section. For a more detailed and complete introduction to game theory, the reader is referred to 
\cite{leyton2008essentials}.  \\
%In section \ref{cha1:FlipItGame} an overview of the FlipIt game is given with the definitions and concepts that will be used throughout the paper. 
%The last section \ref{ch1:extendedWork} will cover the extensions and additions already made on FlipIt. \\
%------------------------------------------------%
%            Intro Game Theory 					 %
%------------------------------------------------%
Game theory is a mathematical way of modelling the interactions between two or more agents where the outcomes depend on what each agent does and and the study of how these interactions should be structured to lead to good outcomes. Game theory therefore has important applications in many areas such as economics, politics, biology, computer science, philosophy and a variety of other disciplines. It gained recognition during the Second World War, when Oskar Morgenstern and John von Neumann both published a book on game theory, titled ``Theory of Games and Economic Behavior'' in 1944 \cite{von1944theory}. This book addressed the mathematical analysis of a series of thinking games. A distinction was made between games in which the strategies and the utility factor of the opponent have no effect on finding the best strategies (e.g. chess) and games wherein this factor does have an influence (e.g. poker). John Nash also played a major role in the history of game theory. He was one of the mathematicians who has formalized game theory. The Nash equilibrium, a common solution concept of a non-cooperative game, was named after him.
~~\\
%Every agent has different levels of happiness for the different outcomes.
%self interested meaning

One of the assumptions underlying game theory is that the players of the game are independent and self-interested. This does not necessarily mean that they want to harm other agents or that they only care about themselves. 
%utility function meaning 
Instead it means that each agent has preferences about which states of the world he likes. These preferences are mapped to natural numbers and are called the utility functions. The numbers are interpreted as a mathematical measure that tells how much an agent likes or dislikes the states of the world. \\
%Cooperative and non cooperative games
%-Remark- Stuk herschrijven-- Payoff introduceren -- zin van wikipedia
%Binnen de speltheorie is een 'spel' een (model van) interactie tussen spelers die individueel beslissingen nemen. De spelers ontvangen een beloning (pay-off) die afhangt van hun eigen beslissingen maar ook van die van de anderen. De volgende typen kunnen worden onderscheiden.
%
%Coöperatieve spellen en niet-coöperatieve spellen[bewerken]
%Het verschil tussen deze twee typen spellen is dat bij coöperatieve spellen (cooperative game theory) bindende afspraken tussen de spelers gemaakt kunnen worden terwijl dit niet mogelijk is bij de niet-coöperatieve spellen (non-cooperative game theory).

In a decision game-theoretic approach an agent will try to act in such a way as to maximize his expected or average utility function. It becomes more complicated when two or more agents want to maximise their utility and when actions of an agent can affect other agents' utilities. In this kind of game, the basic modelling unit is the group of agents. It is referred to as \textit{non-cooperative game theory}. In the individualistic approach the basic modelling is only one agent. This type of game is referred to as \textit{cooperative game theory}.

@@

%John Nash speelde ook een grote rol in de geschiedenis van de speltheorie. Hij is een van de wiskundigen geweest die speltheorie geformaliseerd heeft. Het Nash evenwicht werd naar hem vernoemd. Een Nash evenwicht wordt gezien als een evenwicht tussen beide spelers zodat ze allebei de beste tactiek kiezen en niet meer veranderen als de andere van tactiek veranderen. John Nash breide de theorie over het Nash evenwicht in een paper nog uit met gemengde strategieën. In 1994 kreeg John Nash samen met twee andere wiskundigen gespecialiseerd op het vlak van speltheorie de Nobelprijs voor de economie op basis van hun prestaties in de niet-coöperatieve speltheorie. . Over John Nash is een prachtige film 
\subsubsection{Best response and Nash Equilibrium}
One of the solution concepts in game theory for non-cooperative games that will be used in this paper is a Nash equilibrium. A Nash Equilibrium is a subset of outcomes that can be interesting to analyse a game. To define this concept we first introduce the concept of best response. The best response, given an action of the other player, is the action that maximizes its pay-off.  We define $Opt_{i}$ as the best response function for player \textit{i}. The best response for player \textit{1} is: $a_{1} = Opt_{1}(a_{2})$, given that $a_{2}$ is an action of player 2. For a Nash Equilibrium each player has a list of actions and each player's action maximizes his or her pay-off given the actions of the other players. Nobody has the incentive to independently or unilaterally change his or her action if an equilibrium profile is played. We have a Nash Equilibrium for the pair $(a_{1}^{*},a_{2}^{*})$ when $a_{1}^{*} = Opt_{1}(a_{2}^{*})$ and $a_{2}^{*} = Opt_{2}(a_{1}^{*})$.\\

%-Remark- Matthias: Beter uitleggen: the best response, given an action of the other player, is the action that maximizes its pay-off. Anders lijk je de definitie  v.e. dominante strategie te geven. (Een actie die ongeacht de actie v.d. tegenstander de beste pay-off geeft) Maak onmiddelijk duidelijk dat het een functie van de acties van de tegenstander betreft. Zo is een dominante actie een actie a waarvoor geldt forall a2 : Opt(a2) = a.
% -Remark- Matthias: Hier moet ‘independently’ of ‘one-sidedly’ of ‘unilateraly’ bij staan, anders beschrijf je een dominante strategie. Het mag voor beide beter zijn om gezamelijk te veranderen, maar niet om unilateraal te wijzigen! Kijk maar naar ’t prisoners dilemma: eenzijdig wisselen is slecht voor iedereen in het T/T Nash equilibrium, maar beide weizigen naar S/S zou voor beiden positief zijn!

An example to explain a Nash equilibrium of a two-player game is the prison dilemma. In this game there are two players who are both rational and both of them have committed a crime. `Rational' means that they want the best for themselves and it is not their purpose to do harm to others. Both are locked in a separate room and they cannot tell in advance to each other what they are going to say. Each of them can betray the other or they can support each other and remain silent. If a player confesses, he will either be imprisoned for 3 years or go free, depending on whether the other confesses. If the player is silent, he will either be imprisoned for 5 years or one year, depending on whether the other confesses.  \\ \todo{nakijken met praten, bekennen of andere veraden?}

@@

If there is no feedback for either player, he will play in the same manner against every opponent. The strategy is then called \textit{non-adaptive} because the playing strategy is not dependent on the opponent's movements. An interesting subclass of the non-adaptive strategies is the one where the time intervals between two consecutive moves are generated by a renewal process \todo{renewal beter uitleggen}. An example of such renewal strategy is the periodic strategy where the time between two consecutive moves of the players is a fixed interval. An exponential strategy is a renewal strategy in which the interval between two consecutive moves is exponentially distributed. \\

@@

\subsubsection{Results of the FlipIt game}
The study of the different strategies by means of FlipIt framework allows to derive a number of interesting results \cite{FlipIt}:  
\begin{itemize}
\item periodic strategy strongly dominates the other renewal strategies if the opponent has a periodic or non-arithmetic renewal strategy. This means that it is always advantageous for the opponent to play periodically against a player with a non-adaptive strategy;
\item periodic games are disadvantageous against players following a Last Move adaptive strategy;
\item if a defender facing an LM attacker and with a cost much lower than the attacker, he can play with a periodic rate that is fast enough he'll force the attacker to drop out;
\item a defender facing an LM attacker has to play with a randomized strategy e.g. exponential strategy;
%-Remark- Matthias: Hoe is ‘exponential strategy’ randomized? En uitgebreider spreken over de condities: een defender facing an LM attacker and comparable cost…
\item any amount of feedback about the opponent received during the game, benefits to a player.
\end{itemize}
%-Remark- Matthias: Wat is ‘benefits the player’? Als de speler de feedback negeert benefit die info de speler niet. Ik zou zeggen ‘any amount of feedback about the opponent received during the game allows for better strategies/leads to a better strategy’ ofzo. Let op: Dit is een sterkere/straffere uitspraak, dus denk hier wel goed over na natuurlijk!
